Enforced Invariant Confluence

### 2018-02-15 doc/paper_redux/iconfluence.tex
Progress on dIconfluence and dIreduction.

\section{\Iconfluence{}}
A \emph{distributed object} is a triple $(S, s_0, \join)$ where $S$ is a set of
states, $s_0 \in S$ is a designated start state, and $\join: S \times S \to S$
is a commutative binary merge operator that we call join. A \emph{transaction}
$t: S \to S$ is a function that maps one state to another. An \emph{invariant}
$I: S \to \set{\text{true}, \text{false}}$ is a predicate on states. For
example, $(\nats, +)$ is a distributed object, $t(x) = 2x$ is a transaction,
and $I(x) = x \geq 0$ is an invariant.

@@

Consider any two processors $p_i$ and $p_j$ with states $s_i^0, \ldots, s_i^n$
and $s_j^0, \ldots, s_j^m$ such that every state $s_i^0, \ldots, s_i^n, s_j^0,
\ldots, s_j^m$ satisfies $I$. $T$ is invariant-confluent with respect to $I$,
abbreviated \Iconfluent{}, if $s_i^n \join s_j^m$ is guaranteed to satisfy $I$.

@@

We say an expression $e$ satisfies $I$ if $I(eval(e))$. We say an expression
recursively satisfies $I$, denoted $\Irec{e}$, if $e$ and all of $e$'s children
satisfy $I$. That is,
\begin{mathpar}
  \Irec{s_0} \defeq I(s_0)

  \Irec{t(e)} \defeq I(t(e)) \land I(e)

  \Irec{e_1 \join e_2} \defeq I(e_1 \join e_2) \land I(e_1) \land I(e_2)
\end{mathpar}

We say $T$ is \Iconfluent, if for all expressions $e_1, e_2$, if $\Irec{e_1}$
and $\Irec{e_2}$, then $I(e_1 \join e_2)$.

>>>>

\section{\Iconfluence{}}
A \defword{distributed object} is a triple $(S, s_0, \join)$ where $S$ is a set
of states, $s_0 \in S$ is a designated start state, and $\join: S \times S \to
S$ is a commutative binary merge operator that we call join. A
\defword{transaction} $t: S \to S$ is a function that maps one state to
another.  An \defword{invariant} $I: S \to \set{\text{true}, \text{false}}$ is
a predicate on states. For example, $(\nats, +)$ is a distributed object, $t(x)
= 2x$ is a transaction, and $I(x) = x \geq 0$ is an invariant.

@@

Consider any two processors $p_i$ and $p_j$ with states $s_i^0, \ldots, s_i^n$
and $s_j^0, \ldots, s_j^m$ such that every state $s_i^0, \ldots, s_i^n, s_j^0,
\ldots, s_j^m$ satisfies $I$. $T$ is invariant-confluent with respect to $I$,
abbreviated \defword{\Iconfluent{}}, if $s_i^n \join s_j^m$ is guaranteed to
satisfy $I$.

@@

We say an expression $e$ \defword{satisfies $I$}, denoted $I(e)$, if
$I(eval(e))$. We say an expression \defword{recursively satisfies $I$}, denoted
$\Irec{e}$, if $e$ and all of $e$'s children satisfy $I$. That is,
\begin{mathpar}
  \Irec{s_0} \defeq I(s_0)

  \Irec{t(e)} \defeq I(t(e)) \land \Irec{e}

  \Irec{e_1 \join e_2}
    \defeq I(e_1 \join e_2) \land \Irec{e_1} \land \Irec{e_2}
\end{mathpar}

We say $T$ is \defword{\Iconfluent}, if for all expressions $e_1$ and $e_2$,
$\Irec{e_1}$ and $\Irec{e_2}$ implies $I(e_1 \join e_2)$. From now on, we will
work mostly with the expression-based model of \Iconfluence{}.
